% !TEX program = XeLaTeX
\documentclass[review]{elsarticle}
\usepackage{hyperref}

\begin{document}

Dear Dr. Jim Jansen

Thank you for your consideration, and for reading my manuscript. I have taken this chance to make changes to the manuscript according to your suggestions and comments. 

\begin{itemize}
\item I rewrote my abstract to better highlight the specifics of my findings as you suggested.
\item I added an explicit Research Objective section to the manuscript.
\item I updated my references to newer and more specific research, as well as devling into the relation with information field as you suggested.
\item After checking the \href{https://www.elsevier.com/journals/information-processing-and-management/0306-4573/guide-for-authors}{Guide for Authors} for IPM in Elsevier, I was under the impression that the section \textbf{Your Paper Your Way} meant that the formatting was left for after the reviewing process. Nevertheless, I have complied and formatted the document by using the available LaTeX template.
\item Since I used the LaTeX template, the formatting of my references are all in order now as well.
\item I removed all technical reports from the references and cited them as footnotes when necessary. I believe all the references are either articles in journals or proceedings.
\item I highlited the theoretical and practical implications of my research a bit more on the related work, introduction and abstract of my paper, as they were mostly shown in the discussion part of the article.
\end{itemize}

On the recommendation of reviewers, I believe I will recommend the following people, because of their expertise in use of information science methodology for management applications:

\begin{itemize}
\item Hiroki Sakaji: \\
    Position: Project Lecturer \\
    Institution: University of Tokyo \\
    Email address: sakaji@sys.t.u-tokyo.ac.jp
\item Masaharu Hirota:  \\
	Position: Lecturer \\
	Institution: Okayama University of Science \\
	Email address: hirota@mis.ous.ac.jp
\end{itemize}


I hope this satisfies the requirements for formal review.

\bigskip\bigskip

Regards,

Elisa Claire Alemán Carreón

\end{document}
